---
title: "Mastering Lineplots_LB"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{master-lineplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE
)
```


In this vingette we will see how to master the Lineplots_LB function to build perfect lineplots. First we configure the environment and load all necessary packages. 

```{r setup}
options(scipen = 999999)
library(LandS)
```

After that we can load the dataframe from which we will run the lineplots. 

```{r setup data}
set.seed(2201)
data01 <- data.frame(ID = rep(paste0("PT-", 1:6), each = 5), 
                     Time = rep(1:5, 6), 
                     Marker_1 = rnorm(30), 
                     Marker_2 = rnorm(30, 0, 5), 
                     Marker_3 = rnorm(30, 0, 2), 
                     Gender = factor(rep(c("M", "F"), each = 5, length.out = 30), 
                                     levels = c("M", "F"), ordered = TRUE))
```


In this case the generated data is simulated, for more info on how to set a dataframe compliant with the LandS package consult the "Getting Started" vignette

## Single graph

You can build a single graph using the following code:

```{r single graph}
Lineplots_LB(data = data01, 
             variables = "Marker_1", 
             time = "Time")
```

You can see that the arguments used by the function are: 

- data, the dataframe

- variable, the variable to build the lineplots

- time, the x-axis variable

## Customize a single graph 


We can change the lineplot graphics as follows:

```{r customized single graph}

Lineplots_LB(data = data01, variables = "Marker_1", time = "Time")

```

### Single graph split by a group variable

We can also get separated curves for a specific grouping variable: 

```{r split a single graph}
Lineplots_LB(data = data01, variables = "Marker_1", time = "Time", group = "Gender")
```

## Build a list of lineplots

```{r graphs list}
Lineplots_LB(data = data01, variables = c("Marker_1", "Marker_2"), time = "Time", group = "Gender")
```

## Save a list of lineplots

You can save a list of lineplots in two different ways: you can build a grid and save the entire grid in a pdf file, or you can generate a PPTX file with every lineplot in a different slide. 

### Save a list of lineplots as a pdf grid file

```{r save a list as pdf, eval=FALSE}

List_reg <- Lineplots_LB(data = data01, variables = c("Marker_1", "Marker_2"), time = "Time", group = "Gender")

LandS::Print_LB(plot_list = List_reg, path_print = "your/directory", ext = "pdf")

```
### Save a list of lineplots as a PPTX file

```{r save a list as pptx, eval=FALSE}
Lineplots_LB(data = data01, variables = c("Marker_1", "Marker_2"), time = "Time", group = "Gender", 
             PPTX = TRUE, grid = FALSE, pptx_width = 6, pptx_height = 4, target = "your/directory/new_presentation.pptx")
```

## Customize the colour of the title

```{r custom col title}
library(dplyr)
df_legend <- matrix(ncol = 2, nrow = 2) %>% as.data.frame() %>% `colnames<-`(c("Var", "Colour"))
df_legend$Var <- c("Marker_1", "Marker_2")
df_legend$Colour <- c("red", "orange")

colour_title <- function(i) df_legend$Colour[df_legend$Var == i]

Lineplots_LB(data = data01, variables = c("Marker_1", "Marker_2"), time = "Time", group = "Gender", 
             col_title = TRUE, colour_title = colour_title)
```


## Add overall and posthoc tests to the graphs

```{r test brackets}
# Let's make the grouping variable a factor
data01$Time_fac <- factor(data01$Time, levels = c(1:5), ordered = TRUE)

# Run cont_var_test
Tests <- LandS::cont_var_test_LB(data = data01, variables = c("Marker_1", "Marker_2"), group = "Time_fac", 
                                 paired = TRUE, p.adjust.method = "bonferroni")

Lineplots_LB(data = data01, time = "Time", variables = "Marker_1", Overall = TRUE, Test_results = Tests[[3]], 
             Posthoc = TRUE, posthoc_test_size = 2, threshold_posthoc = 1)

```


## Add extra text to the graphs
